---
title: "Practical Machine Learning"
output: html_document
---

##Synopsis

I explored the data which records numbers about personal activities and tried to predict the ways they lift the barbells. By using the random forest method and 3-fold cross-validation, the overall accuracy of this model is about 96 percents, i.e., 4 percents error rates.

##Data Processing

I first loaded both training data and testing data. According to the testing data, I removed the columns which are not very useful from the data.
```{r,message=FALSE}
library(dplyr)
Training<-read.csv("pml-training.csv",header=TRUE)
Testing<-read.csv("pml-testing.csv",header=TRUE)
SmallTraining<-select(Training, 1:11,37:49,60:68,84:86,102,113:124,140,151:160)
SmallTesting<-select(Testing, 1:11,37:49,60:68,84:86,102,113:124,140,151:160)
SmallerTraining<-select(SmallTraining,8:60)
SmallerTesting<-select(SmallTesting,8:60)
SSmallerTraining<-select(SmallerTraining,1:52)
SSmallerTesting<-select(SmallerTesting,1:52)
```

##Model Fitting

I chose about one-quarter of the data as test data, others are used for training and validation.

```{r}
library(caret)
trainI = sample(1:dim(SSmallerTraining)[1],size=dim(SSmallerTraining)[1]/4*3,replace=F)
trainSA = SSmallerTraining[trainI,]
trainSA0 = SmallerTraining[trainI,]
TtrainSA = SSmallerTraining[-trainI,]
TtrainSA0 = SmallerTraining[-trainI,]
```

For further improve the efficiency, I prepossessed the data using the principal component analysis, which reduced the number of variables more than half.

```{r,message=FALSE}
pre<-preProcess(trainSA,method="pca",thresh=0.80)
train<-predict(pre,trainSA)
test<-predict(pre,TtrainSA)
```

The data is then fitted by the random forest method. For cross-validation, I used the 3-fold method and repeated the process three times.

```{r,message=FALSE,warning=FALSE}
fitControl <- trainControl(method = "repeatedcv",number = 3,repeats = 3)
modelFit<-train(trainSA0$classe ~.,method="rf",trControl = fitControl,data=train)
```

##Result

```{r}
GuessF<-predict(modelFit,test)
confusionMatrix(TtrainSA0$classe,predict(modelFit,test))
```

By using random forest and 3-fold cross-validation, accuracy of this model can achieve about 96 percents. 



